Modal Abstractions for Virtualizing Memory Addresses

### 2023-02-27 programlogic.tex
+

\begin{figure*}
\[
\begin{array}{l}
  \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vpage \stackrel{def}{=} \lambda \crthree.\\
  \exists_{\entryf \;, \entrytr \;, \entrytw \;,\entryo} \ldotp

  \ulcorner \textsf{aligned } \vaddr \urcorner \star  \\
  \nfpointsto{\mask\vaddr\ft\crthree}{\mask\vaddr\tw\crthree}\entryf\qfracfotsss\naddr \star \\ 
   \nfpointsto{\mask\vaddr\ft\entryf}{\mask\vaddr\tw\entryf}\entrytr\qfracfotss\naddr  \star  \\
   \nfpointsto{\mask\vaddr\ft\entrytr}{\mask\vaddr\tw\entrytr}\entrytw\qfracfots\naddr \star \\
  \nfpointsto{\mask\vaddr\ft\entrytw}{\mask\vaddr\tw\entrytw}\entryo\qfracfot\naddr \star \\
   \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr 
\end{array}
\]
\caption{A Strong Virtual Points-to Relation}
\todo[inline]{These fractions aren't quite right (though I see you added the variance between levels), I can walk you through in our meeting tomorrow.}
  \label{fig:strongvirtualpointsto}
\end{figure*}
\end{remark}
%then we reach to a physical page addr (e.g. \textsf{pa}) 
%\[  \paddr\mapsto_{\textsf{a}}\{1\}\vsome \ast \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfrac\naddr \]

@@

\subsection{Address-Space Abstraction}
\label{sec:aspacemodal}
Abstractions we introduce for virtual address spaces are based on two pillars:
\begin{enumerate}
\item a global address space invariant asserting the authorative ownership of the ghost map, , summarizing the existence of the page-table walks, and for each physical page address reached by one of these abstract page-table walks we know that there exists concrete physical page-table accesses, i.e. L4-L1 pointsto
  \item  a modal definition describing the truth of assertions for the resources inside the address space, $[r]P$ indicating that $P$ holds in the virtual address space rooted at $r$.  This is essentially what hybrid logic \ref{} calls a satisfaction operator, which evaluates the truth of a predicate in a named alternative state (here, address space). 
\end{enumerate}
    \subsubsection{Global Per-Addressspace Invariant}

>>>>

\begin{figure*}
  \[
  \begin{array}{l}
\begin{array}{l}
  \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vpage \stackrel{def}{=} \lambda \crthree.\\
  \exists_{\entryf \;, \entrytr \;, \entrytw \;,\entryo} \ldotp

  \ulcorner \textsf{aligned } \vaddr \urcorner \star  \\
  \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo)\\
   \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr 
\end{array} \\

\textsf{where   }\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo) \stackrel{\triangle}{=} \\
 \qquad\qquad \nfpointsto{\mask\vaddr\ft\crthree}{\mask\vaddr\tw\crthree}\entryf\qfracfotsss\naddr \star \\ 
 \qquad\qquad  \nfpointsto{\mask\vaddr\ft\entryf}{\mask\vaddr\tw\entryf}\entrytr\qfracfotss\naddr  \star  \\
  \qquad\qquad \nfpointsto{\mask\vaddr\ft\entrytr}{\mask\vaddr\tw\entrytr}\entrytw\qfracfots\naddr \star \\
  \qquad\qquad \nfpointsto{\mask\vaddr\ft\entrytw}{\mask\vaddr\tw\entrytw}\entryo\qfracfot\naddr 
   \end{array}
\]
\caption{A Strong Virtual Points-to Relation}
\todo[inline]{These fractions aren't quite right (though I see you added the variance between levels), I can walk you through in our meeting tomorrow.}
  \label{fig:strongvirtualpointsto}
\end{figure*}
\end{remark}
%then we reach to a physical page addr (e.g. \textsf{pa}) 
%\[  \paddr\mapsto_{\textsf{a}}\{1\}\vsome \ast \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfrac\naddr \]

@@

\subsection{Address-Space Abstraction}
\label{sec:aspacemodal}
Abstractions we introduce for virtual address spaces are based on two pillars:
\begin{enumerate}
\item a global address space invariant asserting the authorative ownership of the ghost map, $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$ 
\item for each ghost page-table-walk mapping,  $\sumwalkabs\vaddr\qfrac\paddr$, there exists concrete physical page-table accesses path
  \[\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo)\]
  \item  a modal definition describing the truth of assertions for the resources inside the address space, $[r]P$ indicating that $P$ holds in the virtual address space rooted at $r$.  This is essentially what hybrid logic \ref{} calls a satisfaction operator, which evaluates the truth of a predicate in a named alternative state (here, address space). 
\end{enumerate}
    \subsubsection{Global Per-Addressspace Invariant}
